A Technique for Inter-Retailer Recommendations

### 2014-06-11 paper2/paper.tex
Add paper outline at end of intro.

In this report. . . . (BREIFLY OUTLINE THE PAPER HERE.)

>>>>

This report is organized as follows. In the next next section we describe our
dataset and some simple preprocessing that was performed. Next, we outline an
experiment used to simulate the inter-retailer recommendation problem. This is
followed by a section that explains and justifies our evaluation metrics.
Several pages are then dedicated to the details of a novel latent feature
algorithm along with two nontrivial primarily content-based, baseline
recommenders. We then summarize the results of our experiments with these
recommenders along with several additional baseline algorithms.
